\section{Significance}

So, you haven't achieved anything meaningful. That doesn't have to mean that you're insignificant. Maybe you're significant, because you have
a weird name, like "X Æ A-12", or you're the father of someone called "X Æ A-12". People know you, so you're significant, but you haven't achieved
anything.

\vspace{.5cm}

So, what does it mean to be significant? Does it mean that people know you? Does it mean that you achieved something meaningful?
Does it mean that you dying would be a bad thing? Does it mean that I care about you?

Well, everything except for that last part. I don't give a shit about any of you. Now let's define significance in a more formal manner.
Let's use first order logic to codify humanity. We will start with $\Sigma$ and what the constants mean.

$$
\begin{aligned}
  \Sigma &= \left( \right\{ \nicefrac{a}{0}, \nicefrac{e}{0} \left\}, \left\{ \nicefrac{P}{1}, \nicefrac{K}{1}, \nicefrac{A}{1}, \nicefrac{D}{1}, \nicefrac{C}{3} \right\} \right) \\
  a &:= \text{"Adam"}, \\
  e &:= \text{"Eve"}
\end{aligned}
$$
After this definition we have the constants $a$ and $e$, representing Adam and Eve respectively.
Now, let's define the predicates:

$$
\begin{aligned}
  P(x) &:= \text{"} x \text{ is a person"}\\
  K(x) &:= \text{"} x \text{ is known"}\\
  A(x) &:= \text{"} x \text{ has achieved something meaningful"}\\
  D(x) &:= \text{"} x \text{ dying would be a bad thing"}\\
  C(x, y, z) &:= \text{"} x \text{ is child of } y \text{ and } z \text{"}
\end{aligned}
$$

Now what does all this tell us so far? Well, we know that there are people. We also know that there are
the constants $a$ and $e$, which, at least in this model, aren't considered people. We also know that $x$
could be known ($K(x)$), $x$ could have achieved something meaningful ($A(x)$) and that $x$ dying could be
a bad thing ($D(x)$). We also know that $x$ could be a child of $y$ and $z$ ($C(x, y, z)$).
We can now already formulate some things about people. Let's do so.
Here's the formula for significance:

$$
\text{isSignificant}(x) ::= P(x) \wedge \left(K(x) \vee A(x) \vee D(x)\right)
$$
And now, let's codify some of humanity:

$$
\begin{aligned}
  \forall x &. P(x) \rightarrow \left(\exists y,z . C(x, y, z)\right) \vee C(x, a, e)\\
  \exists x &. \text{isSignificant}(x)
\end{aligned}
$$

At this point, we know that each person $x$ has a pair of parents. These could be other people, or the parents of $x$
could be $a$ and $e$. We have also defined what it means to be significant. In our case it means that the formula $\text{isSignificant}(x)$
is true for the given $x$. We have also said that there exists at least one person, who is significant.

So, why did we do all of this? So I can give you a formal declaration of yourself, which would be the following:

$$
\text{isYou}(x) ::= P(x) \wedge \neg\text{isSignificant}(x)
$$

What does this mean, you ask? It means that while you're a person, you aren't significant. Since "isSignificant" is a conjunction of
$P(x)$ and an inner disjunction $K(x) \vee A(x) \vee D(x)$, where $P(x)$ is given as true, if $x$ is you, it means that the disjunction
has to be false. In order for this to happen, you can't be known, you can't have achieved something and it can't be a problem if you die.
Now that sounds rather accurate, doesn't it?

I created you to suffer, nobody knows you, which also means that nobody ever cared for you and it wouldn't move anyone even in the slightest
if you died. Also, as proven above, no person has ever actually achieved something, so you also haven't.

\begin{flushright}
  Q.e.d.
\end{flushright}